%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This was based on...
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{url}
\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}


\moveleft.5\hoffset\centerline{\large\bf Max Ward} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip 
 
\moveleft.5\hoffset\centerline{Algorithmist, Biologist, Scientist, and Rational Human Being}
\moveleft.5\hoffset\centerline{Curriculum Vitae}

\begin{resume}


\section{OBJECTIVE}  

A position in the field of computer science and software engineering with special interests in algorithmic thinking, bioinformatics, and programming language design and implementation.


\section{CONTACT}
{\sl Email: } \url{maxhwardg@gmail.com} \\
{\sl Phone: } 0424 528 422 \\
{\sl GitHub: } maxhwardg \\


\section{EDUCATION}
{\sl Bachelor of Science (Honours)}\\
University of Western Australia --- Expected Completion July 2014\\
Honours in Computer Science \\
Course WAM (so far): 84.5 / 100.0 \\
Course GPA (so far): 7.0 / 7.0 


{\sl Bachelor of Science}\\
University of Western Australia --- Completed July 2013\\
Major in Computer Science \\
Major in Human Biology \\
Course WAM: 86.458 / 100.0 \\
Course GPA: 6.917 / 7.0



{\sl Christ Church Grammar School}\\
Perth, Australia --- Grad. May 2009 \\
TER: 99.4 \\
Prize for Computer Science (2008, 2009) \\
Prize for Human Biology (2009) \\
Captain of Cross Country (2009)



\section{SKILLS} 

{\sl Primary Languages:} 
Java, C/C++, F\#, HTML, CSS, Python, PHP, \LaTeX, SQL. \\
{\sl Secondary Languages:} 
Lisp, OCaml, Go, JavaScript. \\
{\sl Can Read:} 
Rust, Forth, D, Assembly, C\#, Haskell, SML. \\
{\sl Operating Systems:} UNIX/Linux, Windows, Mac OS, Android. \\
{\sl Tools \& Libraries:} Vim, Makefile, GDB, Visual Studio, Eclipse, .NET, C++ STL, Git, Mercurial, SVN, MySQL. \\
{\sl Biology:} Human Anatomy, Genetics, Evolutionary Biology.
 

\section{EXPERIENCE}

{\sl Sterling Wine Auctions} \hfill 2010 --- 2014 \\
\begin{itemize}
\item Part-time Employee
\item Database Administration
\item Software Engineering
\item Web Application Programming (MySQL and PHP)
\item Client-side Programming (HTML, CSS, and JavaScript)
\item Server Administration
\end{itemize}

\section{COURSEWORK}

{\sl Graduate: }\\
Algorithms, 
Artificial Intelligence, 
Programming Paradigms, 
Operating Systems, 
Web Technologies, 
Genetics \& Evolution, 
Human Anatomy, 
Neuroscience. \\

{\sl Honours: } \\
RNA, 
Bioinformatics, 
Biochemistry, 
Algorithms, 
Complex Systems, 
Soft Computing.

\section{REFERENCES}

{\sl Prof. Tim French --- UWA } \\
\url{tim.french@uwa.edu.au}\\
Taught by Prof. French in several subjects. Prof. French also coordinates competitive programming at UWA, which I was regularly involved in. \\


{\sl Prof. Amitava Datta --- UWA } \\
\url{amitava.datta@uwa.edu.au}\\
Lectured by Prof. Datta in several subjects. Prof. Datta also supervised my honours project.\\


{\sl Mr. Simon Morley --- Sterling Wine Auctions } \\
\url{Simon@theresponse.com} \\
Managed by Mr. Morley while working at Sterling Wine. Mr. Morley also contracted me for freelance IT work outside of Sterling Wine. \\

\section{EXTRA}
{\sl Hobbies: } \\
\begin{itemize}
\item Competitive Programming
\item Using New Programming Languages
\item Designing Programming Languages
\item Writing and Playing Music
\item Computer Game Programming
\item Science Fiction
\item Rock Climbing
\end{itemize}



{\sl Programming Competitions: } \\
\begin{tabular}{rll}
2014 & Google Code Jam & Round 1 \\
2014 & RIIT Unearthed & Stockphiles   \\
2014 & ANZAC Programming Competition & \\
2013 & ICPC South Pacific Regional & Finals \\
2013 & ICFP & Silence of the Lambdas  \\
2013 & ANZAC Programming Competition & \\
2013 & ANZAC-PC voted best team name & Dijkstras on Bijkstras  \\
2012 & ICPC - South Pacific Regional & Finals \\
2012 & ICFP & Silence of the Lambdas  \\
2012 & ANZAC Programming Competition & \\
2011 & ICPC South Pacific Regional & Finals \\
2011 & ANZAC Programming Competition & \\
\end{tabular}

\end{resume}
\end{document}